---
title: "Electric Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(reshape)
library(reshape2)
library(highcharter)
```




Revenue
=====================================  


```{r}
revenue <- read.csv("data/total-revenue-from-energy-sold.csv",header = TRUE,stringsAsFactors = FALSE)


#head(consumer)
names(revenue)<- c("Particular","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015")


##Transpose without changing data
m_revenue<-dcast(melt(revenue), ...~Particular)

#renaming
colnames(m_revenue)[colnames(m_revenue)=="variable"] <- "Year"

##Reshaping datasets
melt_revenue <- melt(m_revenue,id=("Year"))


melt_revenue$value<-as.integer(melt_revenue$value)
melt_revenue$Year<- as.character(melt_revenue$Year)
melt_revenue$variable<- as.character(melt_revenue$variable)

hchart(melt_revenue,"line",hcaes(x=Year,y=value,group= variable),color = c("#6c4f70", "#4bd5ee", "#000000", "#008080","#ff0000", "#ffd700", "#0000ff", "#800080","#800000", "#003366", "#00ff00", "#ff00ff","#8b0000", "#ff7f50", "#3b5998"))%>% hc_add_theme(hc_theme_google()) %>%
  hc_title(
    text = "Revenue earned by NEA from Energy sold",
    useHTML = TRUE) %>% 
  hc_subtitle(text="Energy Sold in millions from year 2006 to 2015")%>%
  hc_tooltip(table = TRUE, sort = TRUE) %>% 
  hc_credits(
    enabled = TRUE,
    text = "Source: Data via Opendatanepal",
    href = "http://opendatanepal.com/dataset/total-revenue-from-energy-sold/resource/327b1af5-588c-4935-a546-e2661547893f")
```

Electricity Sales
=====================================  



```{r}
electric.sales<- read.csv("data/total-electricity-sales-2006-to-2015.csv",header = TRUE,stringsAsFactors = FALSE)
names(electric.sales)<- c("Particular","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015")
##Transpose without changing data
m_electric.sales<-dcast(melt(electric.sales), ...~Particular)

#renaming
colnames(m_electric.sales)[colnames(m_electric.sales)=="variable"] <- "Year"

##Reshaping datasets
melt_electric.sales <- melt(m_electric.sales,id=("Year"))
melt_revenue$value<-as.integer(melt_revenue$value)
melt_electric.sales$Year<- as.character(melt_electric.sales$Year)
melt_electric.sales$variable<- as.character(melt_electric.sales$variable)

hchart(melt_electric.sales,"line",hcaes(x=Year,y=value,group=variable),color = c("#000000", "#008080","#ff0000", "#ffd700", "#0000ff", "#800080","#800000", "#003366", "#00ff00", "#ff00ff","#8b0000", "#ff7f50", "#3b5998")) %>% hc_add_theme(hc_theme_google()) %>%
  hc_title(
    text = "Total Electricity Sales from year 2006 to 2015 in Giga Watts Hours",
    useHTML = TRUE) %>% 
  hc_subtitle(text="")%>%
  hc_tooltip(table = TRUE, sort = TRUE) %>% 
  hc_credits(
    enabled = TRUE,
    text = "Source: Data via Opendatanepal",
    href = "http://opendatanepal.com/dataset/total-electricity-sales-2006-to-2015/resource/c562b972-3f65-45e9-9d70-85f07383c8a7")
```

Consumer Growth
=====================================  

```{r}
consumer.growth <- read.csv("data/total-growth-of-electricity-consumers-2006-to-2015.csv",header = TRUE,stringsAsFactors = FALSE)
names(consumer.growth)<- c("Particular","2006","2007","2008","2009","2010","2011","2012","2013","2014","2015")
m_consumer.growth<-dcast(melt(consumer.growth), ...~Particular)
colnames(m_consumer.growth)[colnames(m_consumer.growth)=="variable"] <- "Year"
melt_consumer.growth <- melt(m_consumer.growth,id=("Year"))
melt_revenue$value<-as.integer(melt_revenue$value)
melt_consumer.growth$Year<- as.character(melt_consumer.growth$Year)
melt_consumer.growth$variable<- as.character(melt_consumer.growth$variable)

hchart(melt_consumer.growth,"line",hcaes(x=Year,y=value,group=variable),color = c("#4bd5ee", "#000000", "#008080","#ff0000", "#ffd700", "#0000ff", "#800080","#800000", "#003366", "#00ff00", "#ff00ff","#8b0000", "#ff7f50", "#3b5998")) %>% hc_add_theme(hc_theme_google()) %>%
  hc_title(
    text = "Electricity Consumer Growth  from 2006 to 2015",
    useHTML = TRUE) %>% 
  hc_subtitle(text="")%>%
  hc_tooltip(table = TRUE, sort = TRUE) %>% 
  hc_credits(
    enabled = TRUE,
    text = "Source: Data via Opendatanepal",
    href = "http://opendatanepal.com/dataset/total-growth-of-electricity-consumers-2006-to-2015/resource/9b97e1f9-abb4-40e3-a372-c0079d779815")

```

About
=====================================  

This Dashboard is about the visuaization of the Electric Sales,Customer Growth and Revenue Genearted by the [Nepal Electricity Authority](http://www.nea.org.np/). The data used in this dashboard is from [Open Data Nepal](http://opendatanepal.com/) which has lots of data about Nepal.

This application allows visitors to explore this visualization interactively and learn about the Sales,Customer growth and Revenue over Years. You can click on the legend and remove the graph of the respective values from the Visualization. 


The application is built with the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package for the R programming language.The other packages used for creating this application is [dplyr](https://dplyr.tidyverse.org/) ,reshape, [highcharter](http://jkunst.com/highcharter/) and hosted on [GitHub](https://github.com/).

Code for the application is available at https://github.com/sdiwash/Electric-Dashboard.

I welcome feedback and suggestions! Please visit my [personal website](https://diwashrestha.com/) for contact information or connect with me on [Twitter](https://twitter.com/diwastha).



